---
title: "p8105_hw4_wl2829"
author: "Wentong"
date: "11/14/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
```


## Problem1
&nbsp;
&nbsp;

&nbsp;
&nbsp;



## Problem 2
### a) Generate descriptive statistics for each group and comment on the differences observed.
```{r, results='hide'}
cbp_ptsd = 
  read_csv("./data/Crash.csv")
```

The mean PTSD score of each type of crash
```{r}
lapply(cbp_ptsd, mean, na.rm = T)
```

The mode PTSD score of each type of crash

```{r}
modefunc = function(x){
    tabresult = tabulate(x)
    themode = which(tabresult == max(tabresult))
    if(sum(tabresult == max(tabresult))>1) themode = NA
    return(themode)
}

apply(cbp_ptsd, 2, modefunc)
```

The median PTSD score of each type of crash
```{r}
cbp_ptsd %>% 
  boxplot()
```

```{r}
summary(cbp_ptsd)
```

### b) Using a type I error of 0.01, obtain the ANOVA table. State the hypotheses, test statistic, critical value, and decision interpreted in the context of the problem.
```{r}
cbp_anova = 
  cbp_ptsd %>% 
  pivot_longer(
    pedestrian:car,
    names_to = "group",
    values_to = "score"
  ) %>% 
  na.omit() %>% 
  mutate(group = factor(group))

res_aov = aov(score ~ group, data = cbp_anova)

summary(res_aov)
```

### c) Based on your response in part b), perform pairwise comparisons with an appropriate adjustment (e.g., Bonferroni, Tukey, and Dunnett – ‘below average’ as reference). Report your findings.
```{r}
pairwise.t.test(cbp_anova$score, cbp_anova$group, p.adjust.method="bonferroni")

```


## Problem 3
### a) Justify the appropriate test to be used for addressing the question of interest.
&nbsp;
&nbsp;

### b) Provide the table with all values necessary for calculating the test statistic.
&nbsp;
&nbsp;

### c) State the hypotheses, test statistic, critical value, p value and decision rule interpreted in the context of the problem.




